NumPy---Array Programming in Python

### 2020-02-05 body.tex
Acknowledge Numeric/Numarray developers

Two Python array packages existed before NumPy.
The Numeric package began in the mid-90s and provided an array object in
Python, written in C, and linking to standard fast implementations of linear
algebra \cite{Numericmanual}.
Around 2000, the Space Telescope Science Institute (STScI) software group wrote
a reimplementation of much of Numeric, called NumArray, to support their work
on large memory-mapped arrays and arrays of mixed data type
records \cite{greenfield2003numarray}.
This briefly caused the two communities to diverge, until
2005, when NumPy emerged as a ``best of both worlds'' unification of Numeric
and NumArray \cite{oliphant2006guide}.

>>>>

Two Python array packages existed before NumPy.
The Numeric package began in the mid-90s and provided an array object in
Python, written in C, and linking to standard fast implementations of linear
algebra \cite{Numericmanual}.
Around 2000, the Space Telescope Science Institute (STScI) software group wrote
a reimplementation of Numeric, called NumArray, to support their work
on large memory-mapped arrays and arrays of mixed data type
records \cite{greenfield2003numarray}.
This briefly caused the two communities to diverge, until
2005, when NumPy emerged as a ``best of both worlds'' unification of Numeric
and NumArray \cite{oliphant2006guide}.

### 2020-02-05 paper.tex
Move figure
Minor edits
Acknowledge Numeric/Numarray developers

\usepackage{etoolbox}
\makeatletter
\patchcmd{\@maketitle}
 {\noindent
{\parbox{\dimexpr\linewidth-2\fboxsep\relax}{\color{color1}\large\sffamily\textbf{ABSTRACT}}}}
 {\noindent
{\parbox{\dimexpr\linewidth-2\fboxsep\relax}{\color{color1}\large\sffamily\textbf{ABSTRACT}}}}
 {}{}
\makeatother

@@

S.J.v.d.W and K.J.M. were funded in part by the Gordon and Betty Moore
Foundation through Grant GBMF3834 and by the Alfred P. Sloan Foundation through
Grant 2013-10-27 to the University of California, Berkeley.
S.J.v.d.W, S.B., T.J.R., and W.W. were funded in part by the Gordon
and Betty Moore Foundation through Grant GBMF5447 and by the Alfred
P. Sloan Foundation through Grant G-2017-9960 to the University of
California, Berkeley.

@@

%C.R.H and T.E.O.
S.J.v.d.W and K.J.M. composed the manuscript with input from others.
S.B., K.S., T.J.R., W.W., and M.B. drafted sections.
All authors have contributed significant code, documentation, and/or expertise
to the NumPy project.
All authors reviewed the manuscript.

>>>>

@@

S.J.v.d.W and K.J.M. were funded in part by the Gordon and Betty Moore
Foundation through Grant GBMF3834 and by the Alfred P. Sloan Foundation through
Grant 2013-10-27 to the University of California, Berkeley.
S.J.v.d.W, S.B., M.P., and W.W. were funded in part by the Gordon
and Betty Moore Foundation through Grant GBMF5447 and by the Alfred
P. Sloan Foundation through Grant G-2017-9960 to the University of
California, Berkeley.

Ross Barnowski and Michael Eickenberg suggested text and provided 
helpful feedback.

We would like to thank Jim Hugunin, Paul Dubois, Travis Oliphant, David Ascher,
Tim Peters, Konrad Hinsen, and other Numeric developers.
We would also like to thank Perry Greenfield, Jay Todd Miller, JT Hsu, Richard
L White, Jochen Krupper, Phil Hodge, and other Numarray developers.

Finally, we would like to thank the many members of the community who have provided
feedback, submitted bug reports, made minor improvements to the documentation,
code, or website, promoted its use in their scientific fields, and built
the vast ecosystem of tools and libraries around NumPy.

@@

K.J.M. and S.J.v.d.W composed the manuscript with input from others.
S.B., R.G., K.S., W.W., M.B., and T.J.R. contributed text.
All authors have contributed significant code, documentation, and/or expertise
to the NumPy project.
All authors reviewed the manuscript.
